Estimating excess bereavement due to Covid-19 around the world

### 2020-05-18 covid proposal/archive/20200518/alburez_covid_proposal.Rmd
first word draft

---
title: 'Estimating excess bereavement due to Covid-19'
subtitle: 'Proof of concept for Volkswagen "Corona Crisis and Beyond – Perspectives for Science, Scholarship and Society" grant'
author: "Diego Alburez-Gutierrez, Ivan Williams, and Emilio Zagheni (?)"
date: "15 May 2019"
output:
  pdf_document:
    fig_caption: yes
header-includes: \usepackage{todonotes}
bibliography: bib.bibtex
urlcolor: blue
---

>>>>

---
title: 'Estimating excess bereavement due to Covid-19 around the world'
subtitle: 'Proof of concept for Volkswagen "Corona Crisis and Beyond – Perspectives for Science, Scholarship and Society" grant'
author: "Diego Alburez-Gutierrez, Ivan Williams, and Emilio Zagheni (?)"
date: "15 May 2019"
output:
  pdf_document:
    fig_caption: yes
header-includes: \usepackage{todonotes}
bibliography: bib.bibtex
urlcolor: blue
---
